### 2025-02-21 paper/intro.tex
Small tweaks.
Fix intro.

The idealist inside of us is exasperated, because there should be a perfect
solution that caters for both cases.  However, the practitioner within us
proposes a different perspective.
Instead of using a single language, we may use two languages
in cooperation.  Specifically, we envision an alliance between a
proof assistant and some high-performance language of our choice.

@@

We follow~\cite{cnn-array} which demonstrates that it is possible to implement
one of the canonical convolutional neural network (CNN) in the array
language SaC~\cite{sac1, sac2}, obtaining good sequential and parallel performance
that is competitive with TensorFlow~\cite{ad-tf} and PyTorch~\cite{ad-pytorch}.
Focussing on correctness, we propose
a theory of rank-polymorphic arrays~\cite{rank-poly} in Agda~\cite{agda-2-6-3}.
Within this framework, we encode the CNN from~\cite{cnn-array} and lift it 
into an embedded DSL.  We implement AD
(reverse mode) and domain-specific optimisations for expressions in that DSL.
Finally, we implement an extraction 
into SaC (functional array language) and C (low-level imperative language).

@@

The contributions of this paper are as follows:
\begin{enumerate}
  \item a rank-polymorphic array theory in Agda;
  \item an implementation of the CNN from~\cite{cnn-array} in Agda;
  \item an embedded DSL in Agda which supports AD (reverse mode);
  \item an extraction mechanism for generating SaC or C code from the DSL; and
  \item an experimental evaluation of the generated codes.
\end{enumerate}

>>>>

The idealist inside of us is exasperated, because there should be a perfect
solution that caters for both cases.  However, the practitioner within us
proposes a different perspective.
Instead of using a single language, we may use two languages
in cooperation.  Specifically, we envision an alliance between a
proof assistant, from which we extract code for some high-performance language of our choice.

@@

We follow~\cite{cnn-array} which demonstrates that it is possible to implement
one of the canonical convolutional neural network (CNN) in the array
language SaC~\cite{sac1, sac2}, obtaining good sequential and parallel performance
that is competitive with TensorFlow~\cite{ad-tf} and PyTorch~\cite{ad-pytorch}.
Focussing on correctness, we propose
a theory of rank-polymorphic arrays~\cite{rank-poly} in Agda~\cite{agda-2-6-3}.
Within this framework, we encode the CNN from~\cite{cnn-array} and lift it 
into an embedded DSL.  We implement AD
(reverse mode) and domain-specific optimisations for expressions in that DSL.
Finally, we implement an extraction 
into Futhark (a functional array language) and compare performance with TensorFlow.

@@

The contributions of this paper are as follows:
\begin{enumerate}
  \item a rank-polymorphic array theory in Agda;
  \item an implementation of the CNN from~\cite{cnn-array} in Agda;
  \item an embedded DSL in Agda which supports AD (reverse mode);
  \item an extraction mechanism for generating Futhark code from the DSL; and
  \item an experimental evaluation of the generated codes.
\end{enumerate}
